Title Goes Here

### 2021-04-08 analysis/paper/shceof.Rmd
Agrega referencia a teleconexión

Figure\ \@ref(fig:sst-psi-2) shows regression maps between cEOF2 and Sea Surface Temperatures (SST) Streamfunction at 200 hPa. The Imaginary cEOF2 is associated with strong positive SST anomalies on the Central Pacific and negative anomalies on an area across the North of Australia and New Zealand, the South Pacific Convergence Zone (SPCZ) (Figure\ \@ref(fig:sst-psi-2).a2). This pattern is almost canonically positive ENSO and indeed, the correlation between the Imaginary cEOF2 and the Oceanic Niño Index [@bamston1997] is very high `r enso_cor[cEOF == "cEOF2" & part == "Imaginary"]$text`. Streamfunction anomalies show a coherent picture. The Imaginary cEOF2 is associated with strong wave-like streamfunction anomalies emanating from the tropics (Figure\ \@ref(fig:sst-psi-2).b2). This is consistent with what we know of the effect of ENSO on the extratropics: SST anomalies initiate anomalous convection that excites Rossby waves that propagate meridionally towards higher latitudes \textcolor{red}{(REFS??)}.

Since the Real cEOF2 represents just a different phase of the same wave train, one would expect that it would show a similar forcing pattern to the Imaginary cEOF with a slight translation of its location. However, Figure\ \@ref(fig:sst-psi-2).a1 and b1 show that the Real cEOF2 is not associated either with any significant SST nor streamfunction anomalies in the tropics. The correlation between the Real cEOF2 and ENSO is also not significant (`r enso_cor[cEOF == "cEOF2" & part == "Real"]$text`) \textcolor{red}{(No aparece el valor en el PDF)}. This lack of tropical signal suggests different natures of the different phases of the cEOF2 wave train.

>>>>

Figure\ \@ref(fig:sst-psi-2) shows regression maps between cEOF2 and Sea Surface Temperatures (SST) Streamfunction at 200 hPa. The Imaginary cEOF2 is associated with strong positive SST anomalies on the Central Pacific and negative anomalies on an area across the North of Australia and New Zealand, the South Pacific Convergence Zone (SPCZ) (Figure\ \@ref(fig:sst-psi-2).a2). This pattern is almost canonically positive ENSO and indeed, the correlation between the Imaginary cEOF2 and the Oceanic Niño Index [@bamston1997] is very high `r enso_cor[cEOF == "cEOF2" & part == "Imaginary"]$text`. Streamfunction anomalies show a coherent picture. The Imaginary cEOF2 is associated with strong wave-like streamfunction anomalies emanating from the tropics (Figure\ \@ref(fig:sst-psi-2).b2). This is consistent with what we know of the effect of ENSO on the extratropics: SST anomalies initiate anomalous convection that excites Rossby waves that propagate meridionally towards higher latitudes [@mo2000].

Since the Real cEOF2 represents just a different phase of the same wave train, one would expect that it would show a similar forcing pattern to the Imaginary cEOF with a slight translation of its location. However, Figure\ \@ref(fig:sst-psi-2).a1 and b1 show that the Real cEOF2 is not associated either with any significant SST nor streamfunction anomalies in the tropics. The correlation between the Real cEOF2 and ENSO is also not significant (`r enso_cor[cEOF == "cEOF2" & part == "Real"]$text`). This lack of tropical signal suggests different natures of the different phases of the cEOF2 wave train.
